manuscript_figures

### 2024-05-29 scripts/manuscript_figures.Rmd
finished data and figure 2

# Load libraries 
```{r}
library(plyr)
library(dplyr)
library(MuMIn)
library(tidyverse)
library(lme4)
library(broom.mixed)
library(lubridate)
library(ggplot2)
library(patchwork)
library(broom)

@@

@@

# Extract marginal and conditional R-squared
marginal_r2 <- round(r_squared[1], 2)
conditional_r2 <- round(r_squared[2], 2)
p_value <- signif(lmm_tidy$p.value[lmm_tidy$term == "mean_kelp_cover"], 2)

# Create scatter plot
figure.2 <- ggplot(aggregated_data, aes(x = mean_kelp_cover, y = mean_fish_biomass)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE, formula = y ~ x, color = "blue") +
  annotate("text", x = Inf, y = Inf, label = paste0("Marginal R^2 = ", marginal_r2, "\nConditional R^2 = ", conditional_r2, "\np = ", p_value), 
           hjust = 1.1, vjust = 1.1, size = 4, parse = FALSE) +
  labs(x = "Kelp cover (%)", y = "Fish biomass (g/m2)",
       title = "Fish Biomass vs Kelp Cover") +
  theme_classic();figure.2

>>>>

# Load libraries 
```{r}
library(plyr)
library(dplyr)
library(MuMIn)
library(lmerTest)
library(tidyverse)
library(lme4)
library(broom.mixed)
library(lubridate)
library(ggplot2)
library(patchwork)
library(broom)

@@

# Aggregate the data by year, site, and transect and compute mean values
aggregated_data <- merged.dat %>%
  group_by(YEAR, SITE, TRANSECT) %>%
  summarize(mean_fish_biomass = mean(Fish.Biomass..g.m2., na.rm = TRUE),
            mean_kelp_cover = mean(COVER, na.rm = TRUE)) %>%
  ungroup()

@@

# Extract marginal and conditional R-squared
marginal_r2 <- round(r_squared[1], 2)
conditional_r2 <- round(r_squared[2], 2)

# Extract p-value for mean_kelp_cover
p_value_kelp_cover <- summary(lmm_model)$coefficients["mean_kelp_cover", "Pr(>|t|)"]

# Create scatter plot
figure.2 <- ggplot(aggregated_data, aes(x = mean_kelp_cover, y = mean_fish_biomass)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE, formula = y ~ x, color = "blue") +
annotate("text", x = Inf, y = Inf, label = paste0("Marginal R^2 = ", marginal_r2, "\nConditional R^2 = ", conditional_r2, "\np = ", signif(p_value_kelp_cover, 3)), hjust = 1.4, vjust = 1.1, size = 4, parse = FALSE) + # Adjust vjust
  labs(x = "Kelp cover (%)", y = "Fish biomass (g/m2)",
       title = "Fish Biomass vs Kelp Cover") +
  theme_classic();figure.2

# Save the plot to a file
ggsave("output/figures/figure_2.png", plot = figure.2, width = 8, height = 6)
```
